Univariate model using Wilcox Rank Sum test

### 2020-04-27 scripts/31_univariate_lm_wilcox.Rmd
update

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
library(tidyverse)
library(kableExtra)
```

@@

  num_zero_thre <- floor(ncol(pw_fil) * fil_thre)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

```{r}
library(tidyverse)
library(kableExtra)
```

@@

  num_zero_thre <- floor(ncol(pw) * fil_thre)

@@

```{r}
final
```
